---
title: "Activity 15"
author: "Amar Dani"
date: "11/3/22"
output: html_notebook
---
```{r}
library(ggplot2)
library(ggthemes)
```
```{r}
mn_fci <- read.csv("/Users/sandeep/Downloads/R\ Code/minnesota-fci.csv")
```
```{r}
ggplot(data=mn_fci, aes(x=season, y=fci, color=team)) + geom_point() + scale_color_manual(values = c('#236192', '#D31145', '#4F2683', '#154734'))
```
```{r}
ggplot(data=mn_fci, aes(x=season, y=fci, color=team)) + geom_line() +   scale_color_manual(values = c('#236192', '#D31145', '#4F2683', '#154734')) +  guides(color='none') + 
annotate(
  geom = 'text',
  x=2010, y=325, 
  label ="Minnesota Wild",
  color='#154734',
  hjust=0
  )+
annotate(
  geom = 'text',
  x=2008, y=450, 
  label ="Minnesota Vikings",
  color='#4F2683', 
  hjust=0
  )+
annotate(
  geom = 'text',
  x=2007, y=150, 
  label ="Minnesota Twins",
  color='#D31145', 
  hjust=0
  )+
annotate(
  geom = 'text',
  x=2000, y=200, 
  label ="Minnesota Timberwolves",
  color='#236192', 
  hjust=0
  )
```
4. There was an NHL Lockout in which all games were canceled. 

5. Since the the lines are rising, this suggests the cost of attending games of all Minnesotan teams have increased over time. 

6. The Minnesota Twins has seen increases in cost for fans, however, it has tapered off in recent years. The Minnesota Vikings have the highest cost through 2000-2015, they have also had significant incrases for prices for fans. The Timberwolves also have increases in costs for fans across 2000-2015 but for the period 2005-2010, the costs decreased.
```{r}
nhl_fci <- read.csv('/Users/sandeep/Downloads/R\ Code/nhl-fci.csv')
```
```{r}
wild <- read.csv('/Users/sandeep/Downloads/R\ Code/Wild_FCI.csv')
```

```{r}
ggplot(data=nhl_fci, aes(x=Year, y=FCI, group=Team)) + geom_line(color='lightgrey') + geom_line(data=wild, color='darkred')
```
9. The Wild's FCI is average for the league. The cost has not risne nearly as much as other teams in the league.

```{r}
ggplot(data=nhl_fci, aes(x=Year, y=FCI, group=Team)) + geom_line(color='lightgrey', alpha=0.6) + geom_line(data=wild, color='darkred') + theme_bw() + annotate(
  geom = 'text',
  x=2004, y=200, 
  label ="NHL Lockout",
  hjust=0, angle=90
  ) +
labs(
  title='FCI for Teams in the NHL'
) +
theme(
  plot.title = element_text(face='bold',size=20),
  axis.title.x = element_text(face='bold.italic', size=14),
  axis.title.y = element_text(face='bold.italic', size=14)
) 
```
```{r}
ggplot(data=nhl_fci, aes(x=Year, y=FCI, group=Team)) + geom_line(color='lightgrey', alpha=0.6) + geom_line(data=wild, color='darkred') + theme_bw() + annotate(
  geom = 'text',
  x=2003, y=500, 
  label ="NHL Lockout",
  hjust=0
  ) +
labs(
  title='FCI for Teams in the NHL'
) +
theme(
  plot.title = element_text(face='bold',size=20),
  axis.title.x = element_text(face='bold.italic', size=14),
  axis.title.y = element_text(face='bold.italic', size=14)
) + geom_segment(aes(x=2004, y=250, xend=2004, yend=480), linetype='dotted')
```