---
title: "Activity 04"
author: "Amar Dani"
date: "9/20/22"
output: html_notebook
---

```{r}
library(ggplot2)
```
```{r}
tech_csv <- read_csv("/Users/sandeep/Downloads/R\ Code/tech.csv")
```
```{r}
ggplot(data=tech_csv,aes(x=number_text)) + geom_histogram(binwidth=25, color='blue', fill='gray')
```
```{r}
histo <- ggplot(data=tech_csv,aes(x=number_text)) + geom_histogram(binwidth=25, color='blue', fill='gray') + labs(x='Number of text messages sent and received per day') + scale_x_continuous(breaks=seq(0,400,25)) 
histo
```
```{r}
mean(tech_csv$number_text)
median(tech_csv$number_text)
```
```{r}
histo <- ggplot(data=tech_csv,aes(x=number_text)) + geom_histogram(binwidth=25, color='blue', fill='gray') + 
labs(x='Number of text messages sent and received per day') + scale_x_continuous(breaks=seq(0,400,25)) + geom_vline(aes(xintercept=mean(tech_csv$number_text),color='red')) + geom_vline(aes(xintercept=median(tech_csv$number_text),color='blue'))
histo
```
The histogram is **skewed to the right** and is asymmetrical. The variability is quite high as there are a couple of *outliers*. The best measure of the typical is the **median** as it is relatively unaffected by the outliers. 
```{r}
histo2 <- ggplot(data=tech_csv,aes(x=number_text, fill=preference)) + geom_histogram(binwidth=25, position='identity', alpha=0.5) + 
labs(x='Number of text messages sent and received per day') + scale_x_continuous(breaks=seq(0,400,25))
histo2
```
```{r}
histo2 + facet_wrap(~preference, nrow=3)
```
```{r}
histo3 <- ggplot(data = tech_csv, aes(x=age, fill=phone_type)) + geom_histogram(position='identity') + labs(x='Phone types at a given age') +
facet_wrap(~phone_type, nrow=5)

histo3
```
Both Android and Blackberry are skewed to the right. Although iPhone has a tail to the left, there is no one above the age of 70 who owns an iPhone. For Windows phone and Palm there is not enough data to associate the ownership of those particular types of phones with age. Concerning the variability, majority of those sampled were between 30-40 years of age and typically had an Android or Blackberry phone. For all ages we can conclude there is no assciation with age and the type of phone they own. 