---
title: "Activity 21"
date: "11/28/22"
author: "Amar Dani"
output: html_notebook
---

```{r}
library(ggplot2)
library(ggthemes)
library(dplyr)
library(maps)
```
```{r}
mn_demo <- read.csv("/Users/sandeep/Downloads/R\ Code/mn-demographics.csv")
```
```{r}
ggplot(data=mn, aes(x=long, y=lat)) +
  geom_polygon(aes(group=group)) + coord_quickmap()
```
```{r}
head(mn, 10)
```
```{r}
head(mn_demo, 5)
```
5. Just subregion

```{r}
county_demo <- left_join(mn, mn_demo, by="subregion")
```
```{r}
head(county_demo, 5)
```
```{r}
ggplot(data=county_demo, aes(x=long, y=lat)) +
  geom_polygon(aes(group=group, fill=per_poverty), color='grey') + 
  coord_quickmap() +
  scale_fill_gradient(low = 'white',high = 'darkred') + 
  theme_map() +
  labs(
    title = "Percentage of County Population Living in Poverty",
    subtitle = "For Minnesotan Counties (2013)",
    caption = "Minnesota Department of Health (2013)",
    fill = "Percentage"
  ) + 
  theme(
    plot.title = element_text(face = 'bold',size=15),
    plot.subtitle = element_text(size=12),
    plot.caption = element_text(size=8, face='italic',color='grey70', hjust=0),
    legend.title = element_text(size=10, face = 'bold.italic'),
    legend.position = c(0.85,0.07),
  )
```
5. It seems the lowest levels of poverty directly around the Twin Cities. In Ramsey and Hennepin, the poverty levels are higher, but their neighbors have significantly lower levels of poverty.
```{r}
ggplot(data=county_demo, aes(x=long, y=lat, label = subregion)) +
  geom_polygon(aes(group=group, fill=per_poverty), color='grey') + 
  coord_quickmap() +
  scale_fill_gradient(low = 'white',high = 'darkred') + 
  theme_map() +
  labs(
    title = "Percentage of County Population Living in Poverty",
    subtitle = "For Minnesotan Counties (2013)",
    caption = "Minnesota Department of Health (2013)",
    fill = "Percentage"
  ) + 
  theme(
    plot.title = element_text(face = 'bold',size=15),
    plot.subtitle = element_text(size=12),
    plot.caption = element_text(size=8, face='italic',color='grey70', hjust=0),
    legend.title = element_text(size=10, face = 'bold.italic'),
    legend.position = c(0.85,0.07),
  ) + geom_text(size=2.5)
```
6. There is a lot of overlap because of the sheer number of Minnesotan Counties. Also, a lot of the counties' names are repeated because they are repeated in the dataset.

```{r}
cnames = aggregate(cbind(long, lat) ~ subregion, data = county_demo, FUN = function(x) mean(range(x)))
```
```{r}
head(cnames)
```
```{r}
ggplot(data=county_demo, aes(x=long, y=lat, label = subregion)) +
  geom_polygon(aes(group=group, fill=per_poverty), color='grey') + 
  coord_quickmap() +
  scale_fill_gradient(low = 'white',high = 'darkred') + 
  theme_map() +
  labs(
    title = "Percentage of County Population Living in Poverty",
    subtitle = "For Minnesotan Counties (2013)",
    caption = "Minnesota Department of Health (2013)",
    fill = "Percentage"
  ) + 
  theme(
    plot.title = element_text(face = 'bold',size=15),
    plot.subtitle = element_text(size=12),
    plot.caption = element_text(size=8, face='italic',color='grey70', hjust=0),
    legend.title = element_text(size=10, face = 'bold.italic'),
    legend.position = c(0.85,0.07),
  ) + geom_text(data = cnames, size=2.5)
```
```{r}
county_names <- left_join(cnames, mn_demo, by="subregion")
```
```{r}
head(county_names)
```
```{r}
ggplot(data=county_demo, aes(x=long, y=lat, label = subregion)) +
  geom_polygon(aes(group=group, fill=per_poverty), color='grey') + 
  coord_quickmap() +
  scale_fill_gradient(low = 'white',high = 'darkred') + 
  theme_map() +
  labs(
    title = "Percentage of County Population Living in Poverty",
    subtitle = "For Minnesotan Counties (2013)",
    caption = "Minnesota Department of Health (2013)",
    fill = "Percentage"
  ) + 
  theme(
    plot.title = element_text(face = 'bold',size=15),
    plot.subtitle = element_text(size=12),
    plot.caption = element_text(size=8, face='italic',color='grey70', hjust=0),
    legend.title = element_text(size=10, face = 'bold.italic'),
    legend.position = c(0.85,0.07),
  ) + geom_text(data = subset(county_names, per_poverty<7), size=2.5)
```
```{r}
ggplot(data=county_demo, aes(x=long, y=lat, label = subregion)) +
  geom_polygon(aes(group=group, fill=am_indian), color='grey') + 
  coord_quickmap() +
  scale_fill_gradient(low = 'white',high = 'darkred') + 
  theme_map() +
  labs(
    title = "Number of Indians Living in a County",
    subtitle = "For Minnesotan Counties (2013)",
    caption = "Minnesota Department of Health (2013)",
    fill = "Population"
  ) + 
  theme(
    plot.title = element_text(face = 'bold',size=15),
    plot.subtitle = element_text(size=12),
    plot.caption = element_text(size=8, face='italic',color='grey70', hjust=0),
    legend.title = element_text(size=10, face = 'bold.italic'),
    legend.position = c(0.85,0.07),
  ) + geom_text(data = subset(county_names,am_indian>4000), size=2.5)
```

