---
title: "Assignment 06"
author: "Amar Dani"
date: "11/14/22"
output: html_notebook
---
```{r}
library(ggplot2)
library(ggthemes)
library(RColorBrewer)
library(dplyr)
```
```{r}
whotb <- read.csv("/Users/sandeep/Downloads/R\ Code/WHO-TB.csv")
```
```{r}
ggplot(data=whotb, aes(x=Year,y=TB,color=Country)) + geom_line() + guides(color='none') 
```
I had to use guides to remove the legend otherwise you couldn't see the graph
```{r}
ggplot(data=whotb, aes(x=Year,y=TB,color=Country)) + geom_line() + guides(color='none') + facet_wrap(~Region)
```
3. The vast majority of countries in all regions are experiencing fewer deaths due to tuberculosis. There are many countries in which the number of tuberculosis deaths has been near 0 since 2000. On the other hand, there are countries which have seen tuberculosis deaths plummet in their country.

```{r}
seatbnk <- read.csv("/Users/sandeep/Downloads/R\ Code/SEA-TB-NK.csv")
```
```{r}
whotb_sea <- filter(whotb, Region == 'South-East Asia')
head(whotb_sea)
```
```{r}

ggplot(data=whotb_sea, aes(x=Year,y=TB, color=Country)) + geom_line() + guides(color='none') +theme_bw()+ 
  labs(
  x='',
  y='Deaths (per 100,000)',
  title= 'Deaths from Tuberculosis',
  subtitle = 'Inspecting Data from South-East Asian Countries during 2000-2015',
  caption = 'Source: WHO'
) + scale_color_brewer(palette = 'Dark2') + 
  theme(
    plot.title = element_text(face='bold',size=18),
    axis.title.y = element_text(face='bold.italic'),
    plot.caption = element_text(face='italic',color='grey70',size=8,hjust=0)
  )
```
5. All countries except for North Korea has seen their tuberculosis deaths per 100,000 people decrease or stay level. Myanmar had a very death toll from tuberculosis in 2000 which has steeply decreased and now has a death toll higher than its South East Asian counterparts but lower than its 2000 levels.
```{r}
ggplot(data=whotb_sea, aes(x=Year, y=TB, color=Country)) + geom_line(alpha=0.35) + geom_line(data=seatbnk, color='darkred') + guides(color='none') +theme_bw()+ 
  labs(
  x='',
  y='Deaths (per 100,000)',
  title= 'Deaths from Tuberculosis in South-East Asia',
  subtitle = 'North Korea Highlighted in Red, data from 2000-2015',
  caption = 'Source: WHO'
) + 
  annotate(
  geom = 'text',
  x=2013, y=70, 
  label ="North Korea",
  hjust=0,
  color = 'darkred'
) +
  theme(
    plot.title = element_text(face='bold',size=18),
    axis.title.y = element_text(face='bold.italic'),
    plot.caption = element_text(face='italic',color='grey70',size=8,hjust=0)
  )
```
7. Some variables that many effect the death toll of tuberculosis is percentage of population vaccinated and availability of medical care: perhaps number of doctors per capita, hospital beds in a country, and even nearest hopsital.

